Fast Sorting on Modern Computers

### 2005-08-14 docs/tech_report/background.tex
fixed small errors. didnt really get rid of any TODOs
fixed up the references
tidied up some more stuff

\subsubsection{Bimodal}
A 2-bit dynamic predictor is called a bimodal predictor. It is a simple 2-bit
counter, each combination representing a state. In states 00 and 01, not-taken
is predicted; in states 10 and 11, taken is predicted. Each taken prediction
increments the count, to a maximum of 11, and each not-taken prediction
decrements the counter, to a minimum of zero.

@@

An algorithm which is $O(N)$ is said to complete in linear time. An algorithm
which is $O(N^2)$ is said to complete in quadratic time.  $O(NlogN)$ algorithms
may take several orders of magnitude more time than $O(N)$ algorithms, and
typically use the \n{divide-and-conquer} principle, or use a binary tree to
reduce complexity. Quicksort, mergesort and heapsort are all of this type,
whereas elementary sorts, such as insertion sort, selection sort, bubblesort and
shakersort are $O(N^2)$ algorithms. Radixsort is $O(N)$, but can be more
expensive than quicksort, due to the cost of each step. These are discussed in
later chapters. The shellsort we use, called \n{Gonnet Shellsort} has a
complexity of TODO (see \ref{TODO}).

>>>>

\subsubsection{Bimodal}
A 2-bit dynamic predictor is called a bimodal predictor. It is a simple 2-bit
counter, each combination representing a state. In states 00 and 01, not-taken
is predicted; in states 10 and 11, taken is predicted. Each taken prediction
increments the count, to a maximum of 11, and each not-taken prediction
decrements the counter, to a minimum of 00.

@@

An algorithm which is $O(N)$ is said to complete in linear time. An algorithm
which is $O(N^2)$ is said to complete in quadratic time.  $O(NlogN)$ algorithms
may take several orders of magnitude more time than $O(N)$ algorithms, and
typically use the \n{divide-and-conquer} principle, or use a binary tree to
reduce complexity. Quicksort, mergesort and heapsort are all of this type,
whereas elementary sorts, such as insertion sort, selection sort, bubblesort and
shakersort are $O(N^2)$ algorithms. Radixsort is $O(N)$, but can be more
expensive than quicksort, due to the cost of each step. These are discussed in
later chapters. The complexity of shellsort, meanwhile, is quite complex, and is
discussed in \cite{Sedgewick96}.

### 2005-08-14 docs/tech_report/quick.tex
tidied up some more stuff

The results show again that direct mapped caches can perform better than fully
associative ones. This is true in the case of all the quicksorts, as can be seen
in Figures \ref{base quicksort (no median) level 2 misses} to
\ref{multi-quicksort (sequential search) level 2 misses} graph that this is true
in the case of all the quicksorts. As in Section \ref{mergesort replacement
policy}, this is due to the replacement policy of the fully-associative cache.

>>>>

The results show again (see Section \ref{mergesort replacement policy}) that
direct mapped caches can perform better than fully associative ones. This is
true in the case of all the quicksorts, as can be seen in Figures \ref{base
quicksort (no median) level 2 misses} to \ref{multi-quicksort (sequential
search) level 2 misses} graph that this is true in the case of all the
quicksorts. As in Section \ref{mergesort replacement policy}, this is due to the
replacement policy of the fully-associative cache.
